Characterizing subarctic biomes for land surface modeling of pollution and climate risk

### 2021-05-05 VegOzone.tex
Improved fig04 and changed caption accordingly.
Update to latest version of coprnicus style
Fix Aud's name
Restructure and refine abstract

% Advances in Geosciences (adgeo)
% Advances in Radio Science (ars)
% Advances in Science and Research (asr)
% Advances in Statistical Climatology, Meteorology and Oceanography (ascmo)
% Annales Geophysicae (angeo)
% Archives Animal Breeding (aab)
% ASTRA Proceedings (ap)
% Atmospheric Chemistry and Physics (acp)
% Atmospheric Measurement Techniques (amt)
% Biogeosciences (bg)
% Climate of the Past (cp)
% DEUQUA Special Publications (deuquasp)
% Drinking Water Engineering and Science (dwes)
% Earth Surface Dynamics (esurf)
% Earth System Dynamics (esd)
% Earth System Science Data (essd)
% E&G Quaternary Science Journal (egqsj)
% European Journal of Mineralogy (ejm)
% Fossil Record (fr)
% Geochronology (gchron)
% Geographica Helvetica (gh)
% Geoscience Communication (gc)
% Geoscientific Instrumentation, Methods and Data Systems (gi)
% Geoscientific Model Development (gmd)
% History of Geo- and Space Sciences (hgss)
% Hydrology and Earth System Sciences (hess)
% Journal of Bone and Joint Infection (jbji)
% Journal of Micropalaeontology (jm)
% Journal of Sensors and Sensor Systems (jsss)
% Magnetic Resonance (mr)
% Mechanical Sciences (ms)
% Natural Hazards and Earth System Sciences (nhess)
% Nonlinear Processes in Geophysics (npg)
% Ocean Science (os)
% Primate Biology (pb)
% Proceedings of the International Association of Hydrological Sciences (piahs)
% Scientific Drilling (sd)
% SOIL (soil)
% Solid Earth (se)
% The Cryosphere (tc)
% Weather and Climate Dynamics (wcd)
% Web Ecology (we)
% Wind Energy Science (wes)

@@

\Author[1]{Stefanie}{Falk}
\Author[2]{Ane Victoria}{Vollsnes}
\Author[2]{Aud E. B.}{Eriksen}
\Author[3]{Lisa}{Emberson}
\Author[3]{Connie}{O'Neill}
\Author[1]{Frode}{Stordal}
\Author[1]{Terje}{Koren Berntsen}

@@

%% If an author is deceased, please mark the respective author name(s) with a dagger, e.g. "\Author[2,$\dag$]{Anton}{Aman}", and add a further "\affil[$\dag$]{deceased, 1 July 2019}".

%% If authors contributed equally, please mark the respective author names with an asterisk, e.g. "\Author[2,*]{Anton}{Aman}" and "\Author[3,*]{Bradley}{Bman}" and add a further affiliation: "\affil[*]{These authors contributed equally to this work.}".

@@

\begin{abstract}
The subarctic region is likely to be at threat from the combined impacts of climate change and ozone pollution due to its unique atmospheric mixing characteristics (which lead to peak ozone concentrations in spring), the influence of the jet stream on regional climate, and its unique vegetation bio-types that are acclimatized to extremes of cold and midnight sun. Unfortunately, to date, only a very few studies have been conducted to assess the response of vegetation to variations in climate and air pollution profiles, at least by comparison with other parts of Europe. This study looks to fill this knowledge gap by examining trends in climate variables and ozone pollution that have occurred over the past few decades. These climatological and ozone data are used to assess the extent to which two recent years (2018 and 2019) deviate from climatic and pollution norms and how these current (and potentially more frequent future) deviations may influence ozone damage to subarctic vegetation. To this end, the quality of available global and regional ozone reanalysis products for Europe is assessed. The analysis suggests that only the CAMS Regional Air Quality (CAMSRAQ) reanalysis ensemble sufficiently reproduces the observed seasonal cycle while systematically underestimating \chem{O_3} concentration in the region. We find that 2018 is an anomalous warm and bright year (in particular in spring and early summer) with higher than average \chem{O_3} concentrations in April/May and a high number of episodic peak \chem{O_3} concentration above $40\,\unit{ppb}$ in June--August, the latter in part attributable to an increase in forest fires in the Northern Hemisphere as well as warmer and sunnier conditions. We apply a flux-metric to determine ozone risk and damage to vegetation as a function of ozone concentration, climate variables, and species-specific physiology. We find that parameterization of this flux-metric for subarctic vegetation bio-types increases estimates of ozone-induced reduction of total biomass by between $2.5$ and $17.4\,\unit{\%}$ suggesting that the UNECE LRTAP assessments that use generic parameterizations would underestimate ozone risk in this region. We conclude that appropriate parameterization for the growing season, and plant physiological responses to light and temperature are particularly important for accurate modeling of seasonal gas exchange and that efforts should be targeted towards accurately defining subarctic bio-type physiological response to climatic variables to improve regional and global scale biogeochemical cycling under current and future climates.
\end{abstract}

%\copyrightstatement{TEXT}

@@

\begin{figure*}[t]
  %\includegraphics[width=12cm]{ozone_timeseries_fenoscandic_obs.png}
  \includegraphics[width=12cm]{fig04}
  \caption{Time series of ozone observations in northern Fennoscandia (Tab.~\ref{tab:ebas_obs}) (1986--2019). Data from EBAS until December 2018. The hatched areas indicate periods with insufficient quality control according to \citet{NILU2003}.}
  \label{fig:ozone_timesseries_fenoscandic_obs}
\end{figure*}

>>>>

% Advances in Geosciences (adgeo)
% Advances in Radio Science (ars)
% Advances in Science and Research (asr)
% Advances in Statistical Climatology, Meteorology and Oceanography (ascmo)
% Annales Geophysicae (angeo)
% Archives Animal Breeding (aab)
% ASTRA Proceedings (ap)
% Atmospheric Chemistry and Physics (acp)
% Atmospheric Measurement Techniques (amt)
% Biogeosciences (bg)
% Climate of the Past (cp)
% DEUQUA Special Publications (deuquasp)
% Drinking Water Engineering and Science (dwes)
% Earth Surface Dynamics (esurf)
% Earth System Dynamics (esd)
% Earth System Science Data (essd)
% E&G Quaternary Science Journal (egqsj)
% European Journal of Mineralogy (ejm)
% Fossil Record (fr)
% Geochronology (gchron)
% Geographica Helvetica (gh)
% Geoscience Communication (gc)
% Geoscientific Instrumentation, Methods and Data Systems (gi)
% Geoscientific Model Development (gmd)
% History of Geo- and Space Sciences (hgss)
% Hydrology and Earth System Sciences (hess)
% Journal of Bone and Joint Infection (jbji)
% Journal of Micropalaeontology (jm)
% Journal of Sensors and Sensor Systems (jsss)
% Magnetic Resonance (mr)
% Mechanical Sciences (ms)
% Natural Hazards and Earth System Sciences (nhess)
% Nonlinear Processes in Geophysics (npg)
% Ocean Science (os)
% Polarforschung - Journal of the German Society for Polar Research (polf)
% Primate Biology (pb)
% Proceedings of the International Association of Hydrological Sciences (piahs)
% Scientific Drilling (sd)
% SOIL (soil)
% Solid Earth (se)
% The Cryosphere (tc)
% Weather and Climate Dynamics (wcd)
% Web Ecology (we)
% Wind Energy Science (wes)

@@

\Author[1]{Stefanie}{Falk}
\Author[2]{Ane Victoria}{Vollsnes}
\Author[2]{Aud}{Eriksen}
\Author[3]{Lisa}{Emberson}
\Author[3]{Connie}{O'Neill}
\Author[1]{Frode}{Stordal}
\Author[1]{Terje}{Koren Berntsen}

@@

%% If an author is deceased, please mark the respective author name(s) with a dagger, e.g. "\Author[2,$\dag$]{Anton}{Smith}", and add a further "\affil[$\dag$]{deceased, 1 July 2019}".

%% If authors contributed equally, please mark the respective author names with an asterisk, e.g. "\Author[2,*]{Anton}{Smith}" and "\Author[3,*]{Bradley}{Miller}" and add a further affiliation: "\affil[*]{These authors contributed equally to this work.}".

@@

\begin{abstract}
  The unique vegetation biomes of the subarctic region acclimatized to extremes of cold and midnight sun are likely to be at threat from the combined impacts of climate change and increasing ozone (\chem{O_3}) concentrations. The atmospheric and climatic characteristics of the subarctic are known to lead to pronounced peak \chem{O_3} concentrations in spring. To date, only a few studies have been conducted to assess the response of subarctic vegetation to variations in climate and air pollution, at least by comparison with other parts of Europe. This study looks to fill this knowledge gap by examining trends in climate variables and \chem{O_3} concentrations that have occurred over the past few decades. These climatological and \chem{O_3} data are used to assess the extent to which two recent years (2018 and 2019) deviate from climatic and \chem{O_3} concentration norms and how these current (and potentially more frequent future) deviations may influence \chem{O_3} damage to subarctic vegetation. We find that 2018 was an anomalous warm and bright year (in particular in spring and early summer) with higher than average \chem{O_3} concentrations in April/May and a high number of episodic peak \chem{O_3} concentration above $40\,\unit{ppb}$ in June--August, the latter in part attributable to an increase in forest fires in the Northern Hemisphere as well as warmer and sunnier conditions. We apply a flux-metric to determine \chem{O_3} risk and damage to vegetation as a function of \chem{O_3} concentration, climate variables, and species-specific physiology. We find that bespoke parameterizations of plant fuctional types (PFTs) for subarctic vegetation bio-types increase estimates of ozone-induced reduction of total biomass by $2.5$ to $17.4\,\unit{\%}$ in this flux-metric. Our study, suggests that assessments that use generic parameterizations are likely to underestimate the risk of \chem{O_3} damage in this region. We conclude that appropriate parameterization for the growing season, and plant physiological responses to light and temperature are particularly important for accurate modeling of seasonal gas exchange. Efforts should be targeted towards accurately defining subarctic bio-type physiological response to climatic variables to improve regional and global scale biogeochemical cycling under current and future climates.
\end{abstract}

%\copyrightstatement{TEXT}  %% This section is optional and can be used for copyright transfers.

@@

\begin{figure*}[t]
  %\includegraphics[width=12cm]{ozone_timeseries_fenoscandic_obs.png}
  \includegraphics[width=12cm]{fig04}
  \caption{Time series of ozone observations in northern Fennoscandia (Tab.~\ref{tab:ebas_obs}) (1986--2019). Data from EBAS until December 2018. The hatched areas indicate periods with insufficient quality control according to \citet{NILU2003}. (a) Esrange (SWE); (b) Pallas (FIN); (c) Jergul/Karasjok; (d) Svanvik; (e) Janiskoski.}
  \label{fig:ozone_timesseries_fenoscandic_obs}
\end{figure*}
